### 2022-05-16 background.tex
Tiny fixes. Thesis in final mode. COMPLETE.
Fixed typo which made quotation marks disappear

\begin{figure}[ht!]
    \centering
    \subfloat[Plain Recurrent Neural Network (RNN)]{\includegraphics[scale=0.35]{imgs/RNN.png}\label{fig:RNN}}\qquad
    \subfloat[Gated Recurrent Unit (GRU)]{\includegraphics[scale=0.35]{imgs/GRU.png}\label{fig:GRU}}\qquad
    \subfloat[Long Short-Term Memory (LSTM)]{\includegraphics[scale=0.35]{imgs/LSTM.png}\label{fig:LSTM}}\qquad
    \caption{The cells of different Recurrent Neural Network types. $x_t$ represents inputs, $h_t$ and $C_t$ represent hidden layer vectors passed between cells. $\sigma$ and $tanh$ are activation functions. \cite{lopez_rnn_nodate}
    \label{fig:RNNs}}
\end{figure}

@@

\afterpage{%
\begin{figure}
    \centering
    \includegraphics[scale=0.80]{imgs/transformer.png}
    \caption{The transformer architecture. \cite{vaswani_attention_2017}
    \label{fig:transformer}}
\end{figure}
\clearpage
}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.5]{imgs/encoder_decoder.jpeg}
    \caption{The encoder/decoder structure. \cite{nechu_what_2020}
    \label{fig:encoder_decoder}}
\end{figure}

@@

WRF-SOLAR is an NWP model based on WRF specifically designed to model values useful for solar power, including high-frequency irradiance calculations, more accurate solar position algorithms, and more robust aerosol and particle simulations with regard to radiation \cite{jimenez_wrf-solar_2016}.
\section{Previous work}
Lin et al. \cite{lin_temporal_2020} showed that while the more traditional GRUs and LSTMs show good performance on solar power prediction, Temporal Convolutional Neural Networks (TCNN) can achieve even better performance. \textit{\endquote{TCNN is a novel convolutional architecture designed for sequential modelling, which combines causal and dilated convolutions
and residual connections}} \cite{lin_temporal_2020}.

>>>>

\begin{figure}[ht!]
    \centering
    \subfloat[Plain Recurrent Neural Network (RNN)]{\includegraphics[scale=0.35]{imgs/RNN.png}\label{fig:RNN}}\qquad
    \subfloat[Gated Recurrent Unit (GRU)]{\includegraphics[scale=0.35]{imgs/GRU.png}\label{fig:GRU}}\qquad
    \subfloat[Long Short-Term Memory (LSTM)]{\includegraphics[scale=0.35]{imgs/LSTM.png}\label{fig:LSTM}}\qquad
    \caption{The cells of different Recurrent Neural Network types. $x_t$ represents inputs, $h_t$ and $C_t$ represent hidden layer vectors passed between cells. $\sigma$ and $tanh$ are activation functions \cite{lopez_rnn_nodate}.
    \label{fig:RNNs}}
\end{figure}

@@

\afterpage{%
\begin{figure}
    \centering
    \includegraphics[scale=0.70]{imgs/transformer.png}
    \caption{The transformer architecture \cite{vaswani_attention_2017}.
    \label{fig:transformer}}
\end{figure}
\clearpage
}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.5]{imgs/encoder_decoder.jpeg}
    \caption{The encoder/decoder structure \cite{nechu_what_2020}.
    \label{fig:encoder_decoder}}
\end{figure}

@@

WRF-SOLAR is an NWP model based on WRF specifically designed to model values useful for solar power, including high-frequency irradiance calculations, more accurate solar position algorithms, and more robust aerosol and particle simulations with regard to radiation \cite{jimenez_wrf-solar_2016}.
\section{Previous work}
Lin et al. \cite{lin_temporal_2020} showed that while the more traditional GRUs and LSTMs show good performance on solar power prediction, Temporal Convolutional Neural Networks (TCNN) can achieve even better performance. \enquote{\textit{TCNN is a novel convolutional architecture designed for sequential modelling, which combines causal and dilated convolutions
and residual connections}} \cite{lin_temporal_2020}.
